### 2018-12-01 chapters/3-results.tex
readability

No substantial improvements of AUC values were present when combining all
features of all image types (Table~\ref{tab:auc_combinations}). The AUCs were
within range 0.53--0.82 for L1 regularization and within 0.69--0.80 for L2.

@@

In contrast to the use all features, a better model performance was present when
combining the best 1\% features of various image types (T₂w, ADCₘ, ADCₖ, K,
T₂). The best model performance was obtained when selecting the best 1\%
features based on ADCₘ, K and T₂w with AUC (95\% CI) value of 0.88
(0.82--0.95). The combinations of features extracted from DWI parametric maps
(ADCₘ, ADCₖ, K) and those extracted from T₂w and T₂ together with the
feature selection method lead to improved prediction performance regardless of
the regularization algorithm (L1, L2).

>>>>

No substantial improvements of AUC values were present when combining all
features of all image types (Table~\ref{tab:auc_combinations}). The AUCs were
within range 0.53--0.82 with L1 regularization and within 0.69--0.80 with L2.

@@

In contrast to the use all features, a better model performance was present when
combining the best 1\% features of all image types (T₂w, ADCₘ, ADCₖ, K,
T₂). The best performing model with AUC=0.88 was obtained when selecting the
best 1\% features based on ADCₘ, K and T₂w. The combinations of features
extracted from DWI parametric maps (ADCₘ, ADCₖ, K) and those extracted from T₂w
and T₂ together with the feature selection method lead to improved prediction
performance regardless of the regularization method (L1, L2).
